---
title: "Automated content moderation code"
output:
  github_document:
    toc: true
    toc_depth: 2
---

Import a load of stuff

```{r, message = FALSE}
require(irr)
require(boot)
require(tidyverse)
require(pander)
```

## Toxicity

```{r, message = FALSE}
tox <- read_tsv("dat/toxicity_annotated_comments.tsv")
tox.dem <- read_tsv("dat/toxicity_worker_demographics.tsv")
tox.ann <- read_tsv("dat/toxicity_annotations.tsv")
agg <- read_tsv("dat/aggression_annotated_comments.tsv")
agg.dem <- read_tsv("dat/aggression_worker_demographics.tsv")
agg.ann <- read_tsv("dat/aggression_annotations.tsv")

```
 
```{r}
# Join data frames together
tox.ann %>% left_join(tox.dem) -> tox.long
```
## Distribution of average toxicity per worker.
We might want to know what the average worker's toxicity score is.


```{r}
tox.long %>% group_by(worker_id, gender, age_group, education, english_first_language) %>% filter(gender %in% c("male", "female", NA)) %>% summarise(mean.toxicityscore = mean(toxicity_score)) -> tox.workermeans


ggplot(tox.workermeans) + stat_density(aes(mean.toxicityscore)) + ggtitle("Distribution of mean toxicity score") + theme_minimal()
```

```{r}
ggplot(tox.workermeans) + 
  geom_violin(aes(y = mean.toxicityscore, 
                  fill = gender, 
                  x = gender)) + 
  ggtitle("Distribution of mean toxicity score by gender") + 
  theme_minimal()
```

```{r}
ggplot(tox.workermeans) + 
  geom_violin(aes(mean.toxicityscore, 
                  fill = age_group, 
                  x = age_group)) + 
  ggtitle("Distribution of mean toxicity score by age") + 
  theme_minimal()
```

```{r}
ggplot(tox.workermeans) + 
  geom_violin(aes(mean.toxicityscore, 
                  fill = education, 
                  x = education)) + 
  ggtitle("Distribution of mean toxicity score by education") + 
  theme_minimal()
```

```{r}
  ggplot(tox.workermeans) + 
  geom_violin(aes(mean.toxicityscore, 
                  fill = factor(english_first_language), 
                  x = factor(english_first_language))) + 
  ggtitle("Distribution of mean toxicity score by first language") + 
  theme_minimal()
```


### Can we predict who will have a higher mean toxicity score?

Do this over the data with NA's subsetted out.
```{r}
lm(formula = mean.toxicityscore ~ gender + age_group + education + english_first_language,
   data = tox.workermeans %>% na.omit) %>% 
  summary %>% 
  pander(add.significance.stars = T)
```

##  Getting aggressive

```{r}
# Join data frames together
agg.ann %>% left_join(agg.dem) -> agg.long
```
## Distribution of average aggression per worker.
We might want to know what the average worker's aggression score is.


```{r}
agg.long %>% 
  group_by(worker_id, gender, age_group, education, english_first_language) %>% 
  filter(gender %in% c("male", "female", NA)) %>% 
  summarise(mean.aggressionscore = mean(aggression_score)) -> agg.workermeans


ggplot(agg.workermeans) + 
  stat_density(aes(mean.aggressionscore)) + 
  ggtitle("Distribution of mean aggression score") + 
  theme_minimal()
```

```{r}
ggplot(agg.workermeans) + 
  geom_violin(aes(y = mean.aggressionscore, 
                  fill = gender, 
                  x = gender)) + 
  ggtitle("Distribution of mean aggression score by gender") + 
  theme_minimal()
```

```{r}
ggplot(agg.workermeans) + 
  geom_violin(aes(mean.aggressionscore, 
                  fill = age_group, 
                  x = age_group)) + 
  ggtitle("Distribution of mean aggression score by age") + 
  theme_minimal()
```

```{r}
ggplot(agg.workermeans) +
  geom_violin(aes(mean.aggressionscore, 
                  fill = education, 
                  x = education)) + 
  ggtitle("Distribution of mean aggression score by education") +
  theme_minimal()
```

```{r}
  ggplot(agg.workermeans) + 
  geom_violin(aes(mean.aggressionscore, 
                  fill = factor(english_first_language), 
                  x = factor(english_first_language))) + 
  ggtitle("Distribution of mean aggression score by first language") + 
  theme_minimal()
```


### Can we predict who will have a higher mean aggression score?

Do this over the data with NA's subsetted out.
```{r pander}
lm(formula = mean.aggressionscore ~ gender + age_group + education + english_first_language,
   data = agg.workermeans %>% na.omit) %>% 
  summary %>% 
  pander(add.significance.stars = T)
```

<!-- Make dissent metric per comment -->
<!-- ```{r} -->
<!-- tox.long %>% filter(!is.na(gender)) %>%  -->
<!--   group_by(rev_id, gender) %>%  -->
<!--   filter(n() > 1) %>% -->
<!--   mutate(mean.tox = round(mean(toxicity)),  -->
<!--          dissenter = ifelse(toxicity != mean.tox, 1, 0)) %>% -->
<!--   summarise(dissent = sum(dissenter)/n()) -> tox.dissent -->
<!-- ``` -->


<!-- Sum dissent metric per comment -->
<!-- ```{r} -->
<!-- tox.dissent %>% filter(gender == "female")  -> tox.dissent.f -->
<!-- tox.dissent %>% filter(gender == "male")  -> tox.dissent.m -->
<!-- ``` -->



